Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-07 icdm/submission/includes/evaluation.tex
finished intro + modified summary evaluation

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will measur the quality our embeddings by comparing theim  to a human judged dataset of word pairs, based on their similarity. The reader was also given an explanation about the configuration of our network and introduced to the concept of input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.

>>>>

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will measure the quality of our embeddings by comparing theim  to a human judged dataset of word pairs, based on their similarity, i.e wordsim353. The reader was also given an explanation about the configuration of our network and introduced to the concept of input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.

### 2019-05-07 icdm/submission/includes/introduction.tex
finished intro + modified summary evaluation

 This work proposes an approach that uses advanced optimizers and input shuffling to optimize the convergence time of the SGM. In combination both of these techniques allowed us to decrease the convergence time of the SGM. If combined with an optimized throughput these result could lead to an overall decrease in runtime.\\
 The rest of the paper  is structured as follows: section \ref{sec:background}  describes the SGM and its optimizations. Furthermore, we will give an extended explanation of the gradient descent optimizers used in this work. The reader is introduced to our Implementation in Section \ref{sec:contribution}. Results are presented in  Section \ref{sec:results} , where we will also describe used datasets, the measure applied to compare the quality of word embeddings, and finally the empirical results. The last part will focus on the discussion of our results, and possible future work in Section \ref{sec:discussion} followed by a conclusion in Section \ref{sec:conclusion}.

>>>>

This work focused on improving the convergence time of the SGNS. To facilitate our calculations we propose a slightly altered version of the original SNGS, in which we compute the loss for a very large amount, i.e 2000,  of training sample by computing the sum over all training samples in a batch. We combined this batched approach with advanced optimizers and input shuffling to optimize the convergence time of the SGNS. In combination advanced optimizers and input shuffling allowed us to decrease the convergence time of the SGNS. If combined with an optimized throughput these results could lead to an overall decrease in runtime.\\
 The rest of the paper is structured as follows: section \ref{sec:background}  describes the SGM and the SGNS followed by its optimzations in Section \ref{sec:related_work}.  The reader is introduced to our Implementation in Section \ref{sec:contribution}. Furthermore  we will describe the used datasets, the measure applied to compare the quality of word embeddings and input shuffling in Section \ref{sec:evaluation}. Results are presented in  Section \ref{sec:results}. The last part will focus on the discussion of our results, and possible future work in Section \ref{sec:discussion} followed by a conclusion in Section \ref{sec:conclusion}.
